---
title: "Stat 545B Assignment B1"
output: github_document
---
# Milimeter to Inches Conversion Function

```{r}
suppressPackageStartupMessages(library(devtools)) # for devtools package
suppressPackageStartupMessages(library(dplyr)) # for data maniupulation
suppressPackageStartupMessages(library(testthat)) # for testing functions
suppressPackageStartupMessages(library(digest)) #digests outputs for testing 
suppressPackageStartupMessages(library(palmerpenguins)) # for testing a sample tibble
```


Exercise 1

Function - Exercises 1 and 2

```{r}
#' @description The purpose of this function is to convert mm into inches, by the conversion factor of 1/254.
#'
#' @param mm measurement in mm provided.
#' 
#' @return unit conversion of mm into inches.
#' @export 
#'
#' @examples

mm_to_in <- function(mm) {
  inch = mm/254
  return(inch)
}
```

Exercise 3

Examples (Exercise 3)

<p> The following demonstrates an example unit conversion using manual input of 200mm <p>
```{r}
mm_to_in(200)
```

<p> This shows an example using a unit conversion on a column in a dataframe (using penguins and flipper_length_mm) <p>
```{r}
a <- penguins %>%
  mutate(mm_to_in(flipper_length_mm))
a
```
<p> This shows error when trying to convert string values with the function <p>
```{r, error = TRUE}
mm_to_in(fail)
```
Exercise 4

Test Function (Exercise 4)

```{r, error = TRUE}
mm_test_1 <- digest(mm_to_in(124))
mm_test_2 <- digest(mm_to_in(121.12))
mm_test_3 <- digest(mm_to_in(NA))
```


```{r}
test_that("Testing mm_to_in function",{
  expect_equal(
        digest(mm_to_in(124)), 
               mm_test_1)
})
```

```{r}
test_that("Testing mm_to_in function",{
  expect_equal(
        digest(mm_to_in(121.12)), 
               mm_test_2)
})
```

```{r}
test_that("Testing mm_to_in function",{
  expect_equal(
        digest(mm_to_in(NA)), 
               mm_test_3)
})
```
